\pkg{sdmTMB}: An \proglang{R} Package for Fast, Flexible, and User-Friendly Generalized Linear Mixed Effects Models with Spatial and Spatiotemporal Random Fields

### 2023-12-14 doc/paper-jss/sdmTMB-paper.Rnw
Delete empty line

<<dog-utms, echo=TRUE>>=
dat <- add_utm_columns(dat, c("lon", "lat"),
  units = "km", utm_crs = 32609)
dat$log_depth <- log(dat$depth)

mesh <- make_mesh(dat, xy_cols = c("X", "Y"), cutoff = 8)
@

>>>>

<<dog-utms, echo=TRUE>>=
dat <- add_utm_columns(dat, c("lon", "lat"),
  units = "km", utm_crs = 32609)
dat$log_depth <- log(dat$depth)
mesh <- make_mesh(dat, xy_cols = c("X", "Y"), cutoff = 8)
@
